---
title: "Assignment 4"
author: "Neil Noyes"
date: "9/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Return to the `iris` data set included in R.  Examine the distributions of `Sepal.Length` and `Sepal.Width`.  Produce a graph (or two) which represent these distributions.
```{r}
library(tidyverse)

iris %>%
  ggplot(aes(x = Sepal.Width)) +
  geom_histogram(position="identity", colour="grey40", alpha=0.2, bins = 10)

iris %>%
  ggplot(aes(x = Sepal.Length))+
  geom_histogram(position="identity", colour="grey40", alpha=0.2, bins = 5)
```

What can you say about the variation of `Sepal.Length` and `Sepal.Width`

```{r}
iris %>%
  summarize(SW_mean = mean(Sepal.Width),
            SW_median = median(Sepal.Width),
            SL_mean = mean(Sepal.Length),
            SL_median = median(Sepal.Length))
```
  

  **Sepal widths** appear to have a normal distribution where widths of ~3.0cm (variance of +-0.5cm) are most   common with counts >= 30, whereas there are low counts of sepal widths less than ~2.0cm or greater than       ~4.0cm (< 5 counts each).
  
  **Sepal lengths** seem to be clustered around 5-7cm with little variance. 


2. Examine how the categorical variable `Species` affects the distribution of `Sepal.Length` and `Sepal.Width`.  Produce a graph (or two) which shows clearly the relationship you would like to demonstrate.  Can the covariation here help explain some of the patterns we saw in first exploration?



3. Examine the distribution of `Sepal.Width` now for data in only the species *virginica* in the data set.  What can you say about the distribution?