---
title: "Assignment 4"
author: "Neil Noyes"
date: "9/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 :: Return to the `iris` data set included in R.  Examine the distributions of `Sepal.Length` and `Sepal.Width`.  Produce a graph (or two) which represent these distributions.

```{r}
library(tidyverse)

iris %>%
  ggplot(aes(x = Sepal.Width)) +
  geom_histogram(position="identity", colour="grey40", alpha=0.2, bins = 10)

iris %>%
  ggplot(aes(x = Sepal.Length))+
  geom_histogram(position="identity", colour="grey40", alpha=0.2, bins = 10)
```

I don't really think you can conclude very much out of the sepal length's, so I will try a smaller bin width..
```{r}
iris %>%
  ggplot(aes(x = Sepal.Length))+
  geom_histogram(position="identity", colour="grey40", alpha=0.2, bins = 5)
```

This gives us more of a grouping around 5-7cm.

<span style="color: green; font-size: 14pt">*Comments:*  
        This is a good choice for graphs, but make sure all graphs have good labels (titles, axes).
    </span>

## What can you say about the variation of `Sepal.Length` and `Sepal.Width`?

```{r}
iris %>%
  summarize(SW_mean = mean(Sepal.Width),
            SW_median = median(Sepal.Width),
            SL_mean = mean(Sepal.Length),
            SL_median = median(Sepal.Length))
```
  

  **Sepal widths** appear to have a normal distribution where widths of ~3.0cm (variance of +-0.5cm) are most   common with counts >= 30, whereas there are low counts of sepal widths less than ~2.0cm or greater than       ~4.0cm (< 5 counts each).
  
  **Sepal lengths** seem to be clustered around 5-7cm with little variance. 


## 2 :: Examine how the categorical variable `Species` affects the distribution of `Sepal.Length` and  `Sepal.Width`.  Produce a graph (or two) which shows clearly the relationship you would like to demonstrate. 

Sepal Width's by Species
```{r}
iris %>%
  ggplot() +
  geom_histogram(aes(x = Sepal.Width, fill = Species), binwidth = 0.5) +
  facet_wrap(~Species)
```

Sepal Length's by Species
```{r}
iris %>%
  ggplot() +
  geom_histogram(aes(x = Sepal.Length, fill = Species), binwidth = 0.5) +
  facet_wrap(~Species)
```

## Can the covariation here help explain some of the patterns we saw in first exploration?

  **Sepal Widths:**
    The covariation for sepal widths by species follows what we saw for the sepal widths all together; Among      all species, there are the most widths of around that 3.0cm mark.

  **Sepal Lengths:**
    The covariation for sepal lengths by species explains how there wasn't a clear peak for all of the species     together. Setosa averages around 5cm, Versicolor 5.5-6cm, and Virginica 6.5cm, which explains why when the     bin width was reduced, we saw the majority falling in between 5-7cm.

<span style="color: green; font-size: 14pt">*Comments:*  
        Nice graphs!
    </span>

## 3 :: Examine the distribution of `Sepal.Width` now for data in only the species *virginica* in the data set. 

```{r}
iris %>%
  filter(Species == "virginica") %>%
  ggplot() +
  geom_histogram(colour="grey40", alpha=0.2, aes(x = Sepal.Width), binwidth = 0.25)

```

## What can you say about the distribution?

  The distribution has an average of ~3.0cm and is fairly normal. 